Supplementary Information

### 2020-11-09 doc/manuscript/MEE_manuscript_SI.tex

For each core, \(DBH\) can be reconstructed outside-in (based on recent
\(DBH\), subtracting growth recorded in tree rings) or inside-out
(summing \(\Delta r\) from the inside out). We generally gave precedence
to the outside-in approach. Specifically, when \(DBH\) was taken at the
time of coring,\\
At some of our sites where DBH was not taken at the time of coring
(\emph{SCBI},), DBH measurements taken before or slightly after the time
of coring could be used. (see
\href{https://github.com/EcoClimLab/ForestGEO_dendro/issues/19}{issue
\#19 in ForestGEO\_dendro}) If before, \ldots{} If after\ldots{} For all
outside-in reconstructions, if a negative \(DBH\) was predicted\ldots{}

@@

\begin{longtable}{l>{\raggedright\arraybackslash}p{2.5cm}>{\raggedright\arraybackslash}p{2.5cm}>{\raggedright\arraybackslash}p{2.5cm}>{\raggedright\arraybackslash}p{2.5cm}>{\raggedright\arraybackslash}p{2cm}}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{2}{c}{Precipitation response} & \multicolumn{2}{c}{Temperature response} \\
\cmidrule(l{3pt}r{3pt}){2-3} \cmidrule(l{3pt}r{3pt}){4-5}
species & previously observed & observed here & previously observed & observed here & reference\\
\midrule
\addlinespace[1em]
\multicolumn{4}{l}{\textbf{Lilly Dickey Woods, Indiana, USA}}\\
\hspace{1em}LITU & pos. correlations with Jun-Aug PDSI & pos. response to June $PPT$ & neg. response to Jun-Aug $T_{max}$ & neg. response to June $PET$ & Maxwell, Harley, and Robeson 2016\\
\hspace{1em}QUAL & pos. correlations with Jun-Aug PDSI & pos. response to June $PPT$ & neg. response to Jun-Aug $T_{max}$ & neg. response to June $PET$ & Maxwell, Harley, and Robeson 2016\\
\hspace{1em}QUMO & pos. correlations with Jun-Aug PDSI & pos. response to June $PPT$ & neg. response to Jun-Aug $T_{max}$ & neg. response to June $PET$ & Maxwell, Harley, and Robeson 2016\\
\hspace{1em}QUVE & pos. correlations with Jun-Aug PDSI & pos. response to June $PPT$ & neg. response to Jun-Aug $T_{max}$ & neg. response to June $PET$ & Maxwell, Harley, and Robeson 2016\\
 &  &  &  &  & -\\
BEPA & little relationship to ppt within analysis timeframe (exception: pos. corr. with pAug pre); stronger relationship to streamflow and PDSI &  & little relationship to $T_{mean}$ within analysis timeframe (exception: neg. corr. with pJune and cJan $T_{mean}$) &  & Bumann et al. 2019\\
\addlinespace[1em]
\multicolumn{4}{l}{\textbf{Žofín Forest Dynamics Plot, Czech Republic}}\\
\hspace{1em}JUVI & pos. correlations with $PPT$ pJul-cJune &  & neg. correlation to cJun-cJul $T_{mean}$ &  & Aus de Ar et al. 2018\\
\hspace{1em}PIPO & pos. correlations with $PPT$ cApr-cAug &  & neg. correlation to $T_{mean}$ in pJul, pSep, cMay, cJul &  & Aus de Ar et al. 2018\\
\hspace{1em}ABAL & no sig. correlations with June-July $PPT$ & slight concave-down response to p.Jun-p.July $PPT$ frequency & sig. pos. correlation to April T (strongest T correlation) & pos. response to Jan-March $T_{max}$ & Ka$\v{s}$par, Tumajer, Va$\v{s}\'{i}\v{c}$kov$\'{a}$, and $\v{S}$amonil, in review\\
\hspace{1em}FASY & no sig. correlations with June-July $PPT$ & pos. response to p.Jun-p.July $PPT$ frequency & sig. pos. correlation to Jan T (strongest T correlation) & pos. response to Jan-March $T_{max}$ & Ka$\v{s}$par, Tumajer, Va$\v{s}\'{i}\v{c}$kov$\'{a}$, and $\v{S}$amonil, in review\\
\addlinespace[1em]
\multicolumn{4}{l}{\textbf{Scotty Creek, NW Territories, Canada}}\\
\hspace{1em}PIAB & modest pos. correlations (n.s) with June-July $PPT$ & pos. response to p.Jun-p.July $PPT$ frequency & sig. pos. correlation to March T (strongest current-year T correlation) & pos. response to Jan-March $T_{max}$ & Ka$\v{s}$par, Tumajer, Va$\v{s}\'{i}\v{c}$kov$\'{a}$, and $\v{S}$amonil, in review\\
\bottomrule
\end{longtable}
\endgroup{}

@@

\begin{figure}
\centering
\includegraphics{/Users/kteixeira/Dropbox (Smithsonian)/GitHub/EcoClimLab/ForestGEO-climate-sensitivity/results/climwin_plots_combined/NewMexico_pet.png}
\caption{\textbf{Figure S2 \textbar{} Comparison of climwin output
across growth metrics for the temperature variable group at Little
Tesuque (New Mexico, USA).} Here, \emph{climwin} identified potential
evapotranspiration (\(PET\)) as the strongest climate variable across
all three metrics of growth (\(\Delta r\), BAI, \(\Delta AGB\)) and
regardless of whether all cores were included in the analysis, or only
those for which DBH could be reconstructed (\(\Delta r\)-trees with
\(DBH\), BAI, \(\Delta AGB\)).)}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{/Users/kteixeira/Dropbox (Smithsonian)/GitHub/EcoClimLab/ForestGEO-climate-sensitivity/results/climwin_plots_combined/NewMexico_wet_pre.png}
\caption{\textbf{Figure S3 \textbar{} Comparison of climwin output
across growth metrics for the precipitation variable group at Little
Tesuque (New Mexico, USA).} Here, \emph{climwin} identified
precipitation (\(PPT\)) as the strongest climate variable for
\(\Delta r\) and \(BAI\), but precipitation day frequency (\(PDF\)) as
the strongest climate variable for \(\Delta AGB\).}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{/Users/kteixeira/Dropbox (Smithsonian)/GitHub/EcoClimLab/ForestGEO-climate-sensitivity/results/climwin_plots_combined/HarvardForest_pre_wet.png}
\caption{\textbf{Figure S4 \textbar{} Comparison of climwin output
across growth metrics for the precipitation variable group at Harvard
Forest (Massachusetts, USA).} Here, \emph{climwin} identified
precipitation frequency (\(PDF\)) as the strongest climate variable for
\(\Delta r\), but precipitation amount (\(PPT\)) as the strongest
climate variable for \(BAI\) and \(\Delta AGB\). The optimal time window
(circled) also differed across growth metrics.}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=0.75\textwidth,height=\textheight]{/Users/kteixeira/Dropbox (Smithsonian)/GitHub/EcoClimLab/ForestGEO-climate-sensitivity/results/composite_plots/BCI.png}
\caption{\textbf{Figure S5 \textbar{} Best GLS models for Barro Colorado
Island (Panama) for all three growth metrics: \(\Delta r\), \(BAI\), and
\(\Delta AGB\).} Precipitation and temperature group variables are as
selected by \emph{climwin} (p=previous year, c=current year). For each
species, relationships are plotted if included in top model, with
best-fit polynomials plotted with solid lines when both first- and
second-order terms are signficant, dashed lines when only one term is
signficant, and dotted lines when neither is signficant. Transparent
ribbons indicate 95\% confidence intervals. Vertical grey lines indicate
the long-term mean for the climate variable, shading indicates 1 SD.}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=0.75\textwidth,height=\textheight]{/Users/kteixeira/Dropbox (Smithsonian)/GitHub/EcoClimLab/ForestGEO-climate-sensitivity/results/composite_plots/HKK.png}
\caption{\textbf{Figure S6 \textbar{} Best GLS models for Huai Kha
Khaeng (Thailand) for all three growth metrics: \(\Delta r\), \(BAI\),
and \(\Delta AGB\).} Precipitation and temperature group variables are
as selected by \emph{climwin} (p=previous year, c=current year). For
each species, relationships are plotted if included in top model, with
best-fit polynomials plotted with solid lines when both first- and
second-order terms are signficant, dashed lines when only one term is
signficant, and dotted lines when neither is signficant. Transparent
ribbons indicate 95\% confidence intervals. Vertical grey lines indicate
the long-term mean for the climate variable, shading indicates 1 SD.}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=0.75\textwidth,height=\textheight]{/Users/kteixeira/Dropbox (Smithsonian)/GitHub/EcoClimLab/ForestGEO-climate-sensitivity/results/composite_plots/NewMexico.png}
\caption{\textbf{Figure S7 \textbar{} Best GLS models for Little Tesuque
(New Mexico, USA) for all three growth metrics: \(\Delta r\), \(BAI\),
and \(\Delta AGB\).} Precipitation and temperature group variables are
as selected by \emph{climwin} (p=previous year, c=current year). For
each species, relationships are plotted if included in top model, with
best-fit polynomials plotted with solid lines when both first- and
second-order terms are signficant, dashed lines when only one term is
signficant, and dotted lines when neither is signficant. Transparent
ribbons indicate 95\% confidence intervals. Vertical grey lines indicate
the long-term mean for the climate variable, shading indicates 1 SD.}
\end{figure}

@@

{[}\textbf{Figure S8 \textbar{} Best GLS models for Cedar Breaks (Utah,
USA) for all three growth metrics: \(\Delta r\), \(BAI\), and
\(\Delta AGB\).} Precipitation and temperature group variables are as
selected by \emph{climwin} (p=previous year, c=current year). For each
species, relationships are plotted if included in top model, with
best-fit polynomials plotted with solid lines when both first- and
second-order terms are signficant, dashed lines when only one term is
signficant, and dotted lines when neither is signficant. Transparent
ribbons indicate 95\% confidence intervals. Vertical grey lines indicate
the long-term mean for the climate variable, shading indicates 1 SD.{]}

@@

\begin{figure}
\centering
\includegraphics[width=0.75\textwidth,height=\textheight]{/Users/kteixeira/Dropbox (Smithsonian)/GitHub/EcoClimLab/ForestGEO-climate-sensitivity/results/composite_plots/SCBI.png}
\caption{\textbf{Figure S9 \textbar{} Best GLS models for SCBI
(Virginia, USA) for all three growth metrics: \(\Delta r\), \(BAI\), and
\(\Delta AGB\).} Precipitation and temperature group variables are as
selected by \emph{climwin} (p=previous year, c=current year). For each
species, relationships are plotted if included in top model, with
best-fit polynomials plotted with solid lines when both first- and
second-order terms are signficant, dashed lines when only one term is
signficant, and dotted lines when neither is signficant. Transparent
ribbons indicate 95\% confidence intervals. Vertical grey lines indicate
the long-term mean for the climate variable, shading indicates 1 SD.}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=0.75\textwidth,height=\textheight]{/Users/kteixeira/Dropbox (Smithsonian)/GitHub/EcoClimLab/ForestGEO-climate-sensitivity/results/composite_plots/LillyDickey.png}
\caption{\textbf{Figure S10 \textbar{} Best GLS models for Lilly Dickey
Woods (Indiana, USA) for all three growth metrics: \(\Delta r\),
\(BAI\), and \(\Delta AGB\).} Precipitation and temperature group
variables are as selected by \emph{climwin} (p=previous year, c=current
year). For each species, relationships are plotted if included in top
model, with best-fit polynomials plotted with solid lines when both
first- and second-order terms are signficant, dashed lines when only one
term is signficant, and dotted lines when neither is signficant.
Transparent ribbons indicate 95\% confidence intervals. Vertical grey
lines indicate the long-term mean for the climate variable, shading
indicates 1 SD.}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=0.75\textwidth,height=\textheight]{/Users/kteixeira/Dropbox (Smithsonian)/GitHub/EcoClimLab/ForestGEO-climate-sensitivity/results/composite_plots/HarvardForest.png}
\caption{\textbf{Figure S11 \textbar{} Best GLS models for Harvard
Forest (Massachusetts, USA) for all three growth metrics: \(\Delta r\),
\(BAI\), and \(\Delta AGB\).} Precipitation and temperature group
variables are as selected by \emph{climwin} (p=previous year, c=current
year). For each species, relationships are plotted if included in top
model, with best-fit polynomials plotted with solid lines when both
first- and second-order terms are signficant, dashed lines when only one
term is signficant, and dotted lines when neither is signficant.
Transparent ribbons indicate 95\% confidence intervals. Vertical grey
lines indicate the long-term mean for the climate variable, shading
indicates 1 SD.}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=0.75\textwidth,height=\textheight]{/Users/kteixeira/Dropbox (Smithsonian)/GitHub/EcoClimLab/ForestGEO-climate-sensitivity/results/composite_plots/Zofin.png}
\caption{\textbf{Figure S13 \textbar{} Best GLS models for Zofin (Czech
Republic) for all three growth metrics: \(\Delta r\), \(BAI\), and
\(\Delta AGB\).} Precipitation and temperature group variables are as
selected by \emph{climwin} (p=previous year, c=current year). For each
species, relationships are plotted if included in top model, with
best-fit polynomials plotted with solid lines when both first- and
second-order terms are signficant, dashed lines when only one term is
signficant, and dotted lines when neither is signficant. Transparent
ribbons indicate 95\% confidence intervals. Vertical grey lines indicate
the long-term mean for the climate variable, shading indicates 1 SD.}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=0.75\textwidth,height=\textheight]{/Users/kteixeira/Dropbox (Smithsonian)/GitHub/EcoClimLab/ForestGEO-climate-sensitivity/results/composite_plots/ScottyCreek.png}
\caption{\textbf{Figure S14 \textbar{} Best GLS models for Scotty Creek
(NW Territories, Canada) for all three growth metrics: \(\Delta r\),
\(BAI\), and \(\Delta AGB\).} Precipitation and temperature group
variables are as selected by \emph{climwin} (p=previous year, c=current
year). For each species, relationships are plotted if included in top
model, with best-fit polynomials plotted with solid lines when both
first- and second-order terms are signficant, dashed lines when only one
term is signficant, and dotted lines when neither is signficant.
Transparent ribbons indicate 95\% confidence intervals. Vertical grey
lines indicate the long-term mean for the climate variable, shading
indicates 1 SD.}
\end{figure}

>>>>

For each core, \(DBH\) can be reconstructed outside-in (based on recent
\(DBH\), subtracting growth recorded in tree rings) or inside-out
(summing \(RW\) from the inside out). We generally gave precedence to
the outside-in approach. Specifically, when \(DBH\) was taken at the
time of coring,\\
At some of our sites where DBH was not taken at the time of coring
(\emph{SCBI},), DBH measurements taken before or slightly after the time
of coring could be used. (see
\href{https://github.com/EcoClimLab/ForestGEO_dendro/issues/19}{issue
\#19 in ForestGEO\_dendro}) If before, \ldots{} If after\ldots{} For all
outside-in reconstructions, if a negative \(DBH\) was predicted\ldots{}

@@

\begin{longtable}{l>{\raggedright\arraybackslash}p{2.5cm}>{\raggedright\arraybackslash}p{2.5cm}>{\raggedright\arraybackslash}p{2.5cm}>{\raggedright\arraybackslash}p{2.5cm}>{\raggedright\arraybackslash}p{2cm}}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{2}{c}{Precipitation response} & \multicolumn{2}{c}{Temperature response} \\
\cmidrule(l{3pt}r{3pt}){2-3} \cmidrule(l{3pt}r{3pt}){4-5}
species & previously observed & observed here & previously observed & observed here & reference\\
\midrule
\addlinespace[1em]
\multicolumn{4}{l}{\textbf{Lilly Dickey Woods, Indiana, USA}}\\
\hspace{1em}LITU & pos. correlations with Jun-Aug PDSI & pos. response to June $PPT$ & neg. response to Jun-Aug $T_{max}$ & neg. response to June $PET$ & Maxwell, Harley, and Robeson 2016\\
\hspace{1em}QUAL & pos. correlations with Jun-Aug PDSI & pos. response to June $PPT$ & neg. response to Jun-Aug $T_{max}$ & neg. response to June $PET$ & Maxwell, Harley, and Robeson 2016\\
\hspace{1em}QUMO & pos. correlations with Jun-Aug PDSI & pos. response to June $PPT$ & neg. response to Jun-Aug $T_{max}$ & neg. response to June $PET$ & Maxwell, Harley, and Robeson 2016\\
\hspace{1em}QUVE & pos. correlations with Jun-Aug PDSI & pos. response to June $PPT$ & neg. response to Jun-Aug $T_{max}$ & neg. response to June $PET$ & Maxwell, Harley, and Robeson 2016\\
\addlinespace[1em]
\multicolumn{4}{l}{\textbf{Harvard Forest, Massachusetts, USA}}\\
\hspace{1em} &  &  &  &  & -\\
\addlinespace[1em]
\multicolumn{4}{l}{\textbf{Niobrara and Hansley, Nebraska, USA}}\\
\hspace{1em}BEPA & little relationship to ppt within analysis timeframe (exception: pos. corr. with pAug pre); stronger relationship to streamflow and PDSI &  & little relationship to $T_{mean}$ within analysis timeframe (exception: neg. corr. with pJune and cJan $T_{mean}$) &  & Bumann et al. 2019\\
\hspace{1em}JUVI & pos. correlations with $PPT$ pJul-cJune &  & neg. correlation to cJun-cJul $T_{mean}$ &  & Aus de Ar et al. 2018\\
\hspace{1em}PIPO & pos. correlations with $PPT$ cApr-cAug &  & neg. correlation to $T_{mean}$ in pJul, pSep, cMay, cJul &  & Aus de Ar et al. 2018\\
\addlinespace[1em]
\multicolumn{4}{l}{\textbf{Žofín Forest Dynamics Plot, Czech Republic}}\\
\hspace{1em}ABAL & no sig. correlations with June-July $PPT$ & slight concave-down response to p.Jun-p.July $PPT$ frequency & sig. pos. correlation to April T (strongest T correlation) & pos. response to Jan-March $T_{max}$ & Ka$\v{s}$par, Tumajer, Va$\v{s}\'{i}\v{c}$kov$\'{a}$, and $\v{S}$amonil, in review\\
\hspace{1em}FASY & no sig. correlations with June-July $PPT$ & pos. response to p.Jun-p.July $PPT$ frequency & sig. pos. correlation to Jan T (strongest T correlation) & pos. response to Jan-March $T_{max}$ & Ka$\v{s}$par, Tumajer, Va$\v{s}\'{i}\v{c}$kov$\'{a}$, and $\v{S}$amonil, in review\\
\hspace{1em}PIAB & modest pos. correlations (n.s) with June-July $PPT$ & pos. response to p.Jun-p.July $PPT$ frequency & sig. pos. correlation to March T (strongest current-year T correlation) & pos. response to Jan-March $T_{max}$ & Ka$\v{s}$par, Tumajer, Va$\v{s}\'{i}\v{c}$kov$\'{a}$, and $\v{S}$amonil, in review\\
\hspace{1em} & >700m elev. sites moisture limited June-Aug &  & >700m elev. sites temperature limited except June-Aug &  & Tumajer et al. 2017\\
\addlinespace[1em]
\multicolumn{4}{l}{\textbf{Scotty Creek, NW Territories, Canada}}\\
\hspace{1em} &  &  &  &  & Sniderhan and Baltzer 2016\\
\bottomrule
\end{longtable}
\endgroup{}

@@

\begin{center}\includegraphics[width=0.75\linewidth]{/Users/kteixeira/Dropbox (Smithsonian)/GitHub/EcoClimLab/ForestGEO-climate-sensitivity/results/climwin_plots_combined/NewMexico_pet} \end{center}

\textbf{Figure S2 \textbar{} Comparison of climwin output across growth
metrics for the temperature variable group at Little Tesuque (New
Mexico, USA).} Here, \emph{climwin} identified potential
evapotranspiration (\(PET\)) as the strongest climate variable across
all three metrics of growth (\(RW\), BAI, \(\Delta AGB\)) and regardless
of whether all cores were included in the analysis, or only those for
which DBH could be reconstructed (\(RW\)-trees with \(DBH\), BAI,
\(\Delta AGB\)).

@@

\begin{figure}
\centering
\includegraphics{/Users/kteixeira/Dropbox (Smithsonian)/GitHub/EcoClimLab/ForestGEO-climate-sensitivity/results/climwin_plots_combined/NewMexico_wet_pre.png}
\caption{\textbf{Figure S3 \textbar{} Comparison of climwin output
across growth metrics for the precipitation variable group at Little
Tesuque (New Mexico, USA).} Here, \emph{climwin} identified
precipitation (\(PPT\)) as the strongest climate variable for \(RW\) and
\(BAI\), but precipitation day frequency (\(PDF\)) as the strongest
climate variable for \(\Delta AGB\).}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{/Users/kteixeira/Dropbox (Smithsonian)/GitHub/EcoClimLab/ForestGEO-climate-sensitivity/results/climwin_plots_combined/HarvardForest_pre_wet.png}
\caption{\textbf{Figure S4 \textbar{} Comparison of climwin output
across growth metrics for the precipitation variable group at Harvard
Forest (Massachusetts, USA).} Here, \emph{climwin} identified
precipitation frequency (\(PDF\)) as the strongest climate variable for
\(RW\), but precipitation amount (\(PPT\)) as the strongest climate
variable for \(BAI\) and \(\Delta AGB\). The optimal time window
(circled) also differed across growth metrics.}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=0.75\textwidth,height=\textheight]{/Users/kteixeira/Dropbox (Smithsonian)/GitHub/EcoClimLab/ForestGEO-climate-sensitivity/results/composite_plots/BCI.png}
\caption{\textbf{Figure S5 \textbar{} Best GLS models for Barro Colorado
Island (Panama) for all three growth metrics: \(RW\), \(BAI\), and
\(\Delta AGB\).} Precipitation and temperature group variables are as
selected by \emph{climwin} (p=previous year, c=current year). For each
species, relationships are plotted if included in top model, with
best-fit polynomials plotted with solid lines when both first- and
second-order terms are signficant, dashed lines when only one term is
signficant, and dotted lines when neither is signficant. Transparent
ribbons indicate 95\% confidence intervals. Vertical grey lines indicate
the long-term mean for the climate variable, shading indicates 1 SD.}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=0.75\textwidth,height=\textheight]{/Users/kteixeira/Dropbox (Smithsonian)/GitHub/EcoClimLab/ForestGEO-climate-sensitivity/results/composite_plots/HKK.png}
\caption{\textbf{Figure S6 \textbar{} Best GLS models for Huai Kha
Khaeng (Thailand) for all three growth metrics: \(RW\), \(BAI\), and
\(\Delta AGB\).} Precipitation and temperature group variables are as
selected by \emph{climwin} (p=previous year, c=current year). For each
species, relationships are plotted if included in top model, with
best-fit polynomials plotted with solid lines when both first- and
second-order terms are signficant, dashed lines when only one term is
signficant, and dotted lines when neither is signficant. Transparent
ribbons indicate 95\% confidence intervals. Vertical grey lines indicate
the long-term mean for the climate variable, shading indicates 1 SD.}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=0.75\textwidth,height=\textheight]{/Users/kteixeira/Dropbox (Smithsonian)/GitHub/EcoClimLab/ForestGEO-climate-sensitivity/results/composite_plots/NewMexico.png}
\caption{\textbf{Figure S7 \textbar{} Best GLS models for Little Tesuque
(New Mexico, USA) for all three growth metrics: \(RW\), \(BAI\), and
\(\Delta AGB\).} Precipitation and temperature group variables are as
selected by \emph{climwin} (p=previous year, c=current year). For each
species, relationships are plotted if included in top model, with
best-fit polynomials plotted with solid lines when both first- and
second-order terms are signficant, dashed lines when only one term is
signficant, and dotted lines when neither is signficant. Transparent
ribbons indicate 95\% confidence intervals. Vertical grey lines indicate
the long-term mean for the climate variable, shading indicates 1 SD.}
\end{figure}

@@

{[}\textbf{Figure S8 \textbar{} Best GLS models for Cedar Breaks (Utah,
USA) for all three growth metrics: \(RW\), \(BAI\), and \(\Delta AGB\).}
Precipitation and temperature group variables are as selected by
\emph{climwin} (p=previous year, c=current year). For each species,
relationships are plotted if included in top model, with best-fit
polynomials plotted with solid lines when both first- and second-order
terms are signficant, dashed lines when only one term is signficant, and
dotted lines when neither is signficant. Transparent ribbons indicate
95\% confidence intervals. Vertical grey lines indicate the long-term
mean for the climate variable, shading indicates 1 SD.{]}

@@

\begin{figure}
\centering
\includegraphics[width=0.75\textwidth,height=\textheight]{/Users/kteixeira/Dropbox (Smithsonian)/GitHub/EcoClimLab/ForestGEO-climate-sensitivity/results/composite_plots/SCBI.png}
\caption{\textbf{Figure S9 \textbar{} Best GLS models for SCBI
(Virginia, USA) for all three growth metrics: \(RW\), \(BAI\), and
\(\Delta AGB\).} Precipitation and temperature group variables are as
selected by \emph{climwin} (p=previous year, c=current year). For each
species, relationships are plotted if included in top model, with
best-fit polynomials plotted with solid lines when both first- and
second-order terms are signficant, dashed lines when only one term is
signficant, and dotted lines when neither is signficant. Transparent
ribbons indicate 95\% confidence intervals. Vertical grey lines indicate
the long-term mean for the climate variable, shading indicates 1 SD.}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=0.75\textwidth,height=\textheight]{/Users/kteixeira/Dropbox (Smithsonian)/GitHub/EcoClimLab/ForestGEO-climate-sensitivity/results/composite_plots/LillyDickey.png}
\caption{\textbf{Figure S10 \textbar{} Best GLS models for Lilly Dickey
Woods (Indiana, USA) for all three growth metrics: \(RW\), \(BAI\), and
\(\Delta AGB\).} Precipitation and temperature group variables are as
selected by \emph{climwin} (p=previous year, c=current year). For each
species, relationships are plotted if included in top model, with
best-fit polynomials plotted with solid lines when both first- and
second-order terms are signficant, dashed lines when only one term is
signficant, and dotted lines when neither is signficant. Transparent
ribbons indicate 95\% confidence intervals. Vertical grey lines indicate
the long-term mean for the climate variable, shading indicates 1 SD.}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=0.75\textwidth,height=\textheight]{/Users/kteixeira/Dropbox (Smithsonian)/GitHub/EcoClimLab/ForestGEO-climate-sensitivity/results/composite_plots/HarvardForest.png}
\caption{\textbf{Figure S11 \textbar{} Best GLS models for Harvard
Forest (Massachusetts, USA) for all three growth metrics: \(RW\),
\(BAI\), and \(\Delta AGB\).} Precipitation and temperature group
variables are as selected by \emph{climwin} (p=previous year, c=current
year). For each species, relationships are plotted if included in top
model, with best-fit polynomials plotted with solid lines when both
first- and second-order terms are signficant, dashed lines when only one
term is signficant, and dotted lines when neither is signficant.
Transparent ribbons indicate 95\% confidence intervals. Vertical grey
lines indicate the long-term mean for the climate variable, shading
indicates 1 SD.}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=0.75\textwidth,height=\textheight]{/Users/kteixeira/Dropbox (Smithsonian)/GitHub/EcoClimLab/ForestGEO-climate-sensitivity/results/composite_plots/Zofin.png}
\caption{\textbf{Figure S13 \textbar{} Best GLS models for Zofin (Czech
Republic) for all three growth metrics: \(RW\), \(BAI\), and
\(\Delta AGB\).} Precipitation and temperature group variables are as
selected by \emph{climwin} (p=previous year, c=current year). For each
species, relationships are plotted if included in top model, with
best-fit polynomials plotted with solid lines when both first- and
second-order terms are signficant, dashed lines when only one term is
signficant, and dotted lines when neither is signficant. Transparent
ribbons indicate 95\% confidence intervals. Vertical grey lines indicate
the long-term mean for the climate variable, shading indicates 1 SD.}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=0.75\textwidth,height=\textheight]{/Users/kteixeira/Dropbox (Smithsonian)/GitHub/EcoClimLab/ForestGEO-climate-sensitivity/results/composite_plots/ScottyCreek.png}
\caption{\textbf{Figure S14 \textbar{} Best GLS models for Scotty Creek
(NW Territories, Canada) for all three growth metrics: \(RW\), \(BAI\),
and \(\Delta AGB\).} Precipitation and temperature group variables are
as selected by \emph{climwin} (p=previous year, c=current year). For
each species, relationships are plotted if included in top model, with
best-fit polynomials plotted with solid lines when both first- and
second-order terms are signficant, dashed lines when only one term is
signficant, and dotted lines when neither is signficant. Transparent
ribbons indicate 95\% confidence intervals. Vertical grey lines indicate
the long-term mean for the climate variable, shading indicates 1 SD.}
\end{figure}
